Epistasis is widespread in the genetic control of transcription in humans

### 2013-05-30 docs/manuscript/nature_letter.tex
added new graphs

\subsection{Functional annotation}
Of the 549 interactions, 66 were \emph{cis}-\emph{cis} acting (both SNPs were on the same chromosome as the expression gene), 470 were \emph{cis}-\emph{trans} acting, and 13 were \emph{trans}-\emph{trans} acting. In total the 549 interactions comprised 835 unique SNPs, which we analysed for functional enrichment. We observed that there was significant enrichment of \emph{cis}-acting SNPs in transcriptionally active regions for haematopoetic cell lines only, as measured by localisation within H3K4me3 active regions (the three tissues with the strongest enrichment are significant at $p < 1 \times 10^{-4}$, after adjusting for multiple testing), but \emph{trans}-acting SNPs did not show tissue specific enrichment ($p > 0.1$ for all tissues, Supplementary Figure \ref{fig:h3k4me3}).

@@

\begin{figure}
	\caption{\textbf{Tissue specific enrichment of SNPs in transcriptionally active regions} The locations of transcriptional activity can be predicted by chromatin marks, assayed by H3K4me3. Here we show that there is }
	\label{fig:h3k4me3}
\end{figure}
\clearpage

>>>>

\subsection{Functional annotation}
Of the 549 interactions, 66 were \emph{cis}-\emph{cis} acting (both SNPs were on the same chromosome as the expression gene), 470 were \emph{cis}-\emph{trans} acting, and 13 were \emph{trans}-\emph{trans} acting. In total the 549 interactions comprised 835 unique SNPs, which we analysed for functional enrichment. We observed that there was significant enrichment of \emph{cis}-acting SNPs in transcriptionally active regions for haematopoetic cell lines only, as measured by localisation within H3K4me3 active regions (the three tissues with the strongest enrichment are significant at $p < 1 \times 10^{-4}$, after adjusting for multiple testing, Supplementary Figure \ref{fig:transh3k4me3}), but \emph{trans}-acting SNPs did not show tissue specific enrichment ($p > 0.1$ for all tissues, Supplementary Figure \ref{fig:transh3k4me3}).

@@

\begin{figure}
	\includegraphics[width=5in]{cis_h3k4me3}
	\caption{\textbf{Tissue specific enrichment of SNPs in transcriptionally active regions} The locations of transcriptional activity can be predicted by chromatin marks, assayed by H3K4me3. Here we show that there is }
	\label{fig:cish3k4me3}
\end{figure}

\begin{figure}
	\includegraphics[width=5in]{trans_h3k4me3}
	\caption{\textbf{Tissue specific enrichment of SNPs in transcriptionally active regions} The locations of transcriptional activity can be predicted by chromatin marks, assayed by H3K4me3. Here we show that there is }
	\label{fig:transh3k4me3}
\end{figure}
\clearpage
